Lesson 6
========================================================

### Welcome
Notes:

***

### Scatterplot Review

```{r Scatterplot Review}
ggplot(diamonds, aes(x = carat, y = price)) + scale_x_continuous(lim = c(0, quantile(diamonds$carat, 0.99))) + scale_y_continuous(lim = c(0, quantile(diamonds$price, 0.99))) + geom_point(fill = I('#F79420'), color = I('black'), shape = 21 )
#为什么会有几条浅色的线呢，后续研究

#add liner model
ggplot(diamonds, aes(x = carat, y = price)) + scale_x_continuous(lim = c(0, quantile(diamonds$carat, 0.99))) + scale_y_continuous(lim = c(0, quantile(diamonds$price, 0.99))) + geom_point(color = I('#F79420'), alpha = 1/4) + stat_smooth(method = 'lm')
#shape 21 的话color是图形的边框色，fill是内部色。默认的是一个实心圆
# + 的顺序就是图层的顺序，最后的在最上面
```

***

### Price and Carat Relationship
Response:

***

### Frances Gerety
Notes:

#### A diamonds is


***

### The Rise of Diamonds
Notes:

***

### ggpairs Function
Notes:

```{r ggpairs Function}
# install these if necessary
install.packages('GGally')
install.packages('scales')
install.packages('memisc')
install.packages('lattice')
install.packages('MASS')
install.packages('car')
install.packages('reshape')
install.packages('plyr')
#check packages
library(GGally)
library(scales)
library(memisc)
library(lattice)
library(MASS)
library(car)
library(reshape)
library(reshape2)
library(plyr)

# load the ggplot graphics package and the others
library(ggplot2)
library(GGally)
library(scales)
library(memisc)

# sample 10,000 diamonds from the data set
set.seed(20022012)
diamond_samp <- diamonds[sample(1:length(diamonds$price), 10000), ]
#ggpairs(diamond_samp, params = c(shape = I('.'), outlier.shape = I('.')))
#以上为旧版本ggpairs
ggpairs(diamond_samp, 
  lower = list(continuous = wrap("points", shape = I('.'))), 
  upper = list(combo = wrap("box", outlier.shape = I('.'))))
```

What are some things you notice in the ggpairs output?
Response:

***

### The Demand of Diamonds
Notes:

```{r The Demand of Diamonds}
library(gridExtra)
library(grid)
plot1 <- qplot(data = diamonds, x = price, binwidth = 3, fill = I('orange')) + ggtitle('Price')

ggplot1 <- ggplot()

ggplot(aes(x = cut, y = price/carat), data = diamonds) + geom_point(aes(color = color)) + facet_wrap(~ clarity) + scale_color_brewer(type = 'div')

plot2 <- qplot(data = diamonds, x = price, binwidth = 0.01, fill = I('blue')) + ggtitle('Price(log10)') + scale_x_log10()

ggplot2 <- ggplot()

grid.arrange(plot1, plot2, ncol = 2)
#这里要注意一下前面的如果binwidth = 0.01的话，会输出上千万个点，就死掉了。下面运行的红色按钮可以终结程序
```

***

### Connecting Demand and Price Distributions
Notes:

***

### Scatterplot Transformation

```{r Scatterplot Transformation}
qplot(carat, price, data = diamonds) + scale_y_continuous(trans = log10_trans()) + ggtitle('Price (log10) by Carat')
qplot(carat, price, data = diamonds) + ggtitle('Price (log10) by Carat')

cuberoot_trans = function() trans_new('cuberoot', transform = function(x) x^(1/3), inverse = function(x) x^3)

ggplot(aes(carat, price), data = diamonds) + geom_point(color = 'orange') + scale_x_continuous(trans = cuberoot_trans(), limits = c(0.2,3), breaks = c(0.2, 0.5, 1, 2, 3)) + scale_y_continuous( trans = log10_trans(), limits = c(350, 15000), breaks = c(350, 1000, 5000, 10000, 15000)) + ggtitle('Price (log10) by Cube-Root of Carat')
#limits和breaks的数值是显示时的限制和标尺。
#转换的作用是能够比原图更佳趋于线性，利于线性预测的符合度
```


### Create a new function to transform the carat variable

```{r cuberoot transformation}
cuberoot_trans = function() trans_new('cuberoot', transform = function(x) x^(1/3),
                                      inverse = function(x) x^3)
```

#### Use the cuberoot_trans function
```{r Use cuberoot_trans}
ggplot(aes(carat, price), data = diamonds) + 
  geom_point() + 
  scale_x_continuous(trans = cuberoot_trans(), limits = c(0.2, 3),
                     breaks = c(0.2, 0.5, 1, 2, 3)) + 
  scale_y_continuous(trans = log10_trans(), limits = c(350, 15000),
                     breaks = c(350, 1000, 5000, 10000, 15000)) +
  ggtitle('Price (log10) by Cube-Root of Carat')
```

***

### Overplotting Revisited

```{r Sort and Head Tables}
head(sort(table(diamonds$carat), decreasing = T))
head(sort(table(diamonds$price), decreasing = T))
```


```{r Overplotting Revisited}
ggplot(aes(carat, price), data = diamonds) + 
  geom_point(alpha = 0.2, size = 0.75, position = 'jitter') + 
  scale_x_continuous(trans = cuberoot_trans(), limits = c(0.2, 3),
                     breaks = c(0.2, 0.5, 1, 2, 3)) + 
  scale_y_continuous(trans = log10_trans(), limits = c(350, 15000),
                     breaks = c(350, 1000, 5000, 10000, 15000)) +
  ggtitle('Price (log10) by Cube-Root of Carat')
#可以通过position将jitter放到point中，这样就不用geom_jitter了，比较统一
#钻石的切工是按照总体百分比来定义的，3%-ideal， 15% very good，，，切工间的区别是光是否能够尽量多的进入到钻石中
#https://www.bluenile.com/education/diamonds/cut
```

***

### Other Qualitative Factors
Notes:

***

### Price vs. Carat and Clarity

Alter the code below.
```{r Price vs. Carat and Clarity}
# install and load the RColorBrewer package
#install.packages('RColorBrewer')
library(RColorBrewer)

ggplot(aes(x = carat, y = price, color = clarity), data = diamonds) + 
  geom_point(alpha = 0.5, size = 1, position = 'jitter') +
  scale_color_brewer(type = 'div',
    guide = guide_legend(title = 'Clarity', reverse = T,
    override.aes = list(alpha = 1, size = 2))) +  
  scale_x_continuous(trans = cuberoot_trans(), limits = c(0.2, 3),
    breaks = c(0.2, 0.5, 1, 2, 3)) + 
  scale_y_continuous(trans = log10_trans(), limits = c(350, 15000),
    breaks = c(350, 1000, 5000, 10000, 15000)) +
  ggtitle('Price (log10) by Cube-Root of Carat and Clarity')
#http://ggplot2.tidyverse.org/reference/scale_brewer.html
#scale_color_brewer是一个上色的函数，包含在RColorBrewer库中。
#http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/#palettes-color-brewer
#http://www.cookbook-r.com/Graphs/Legends_(ggplot2)/
#scale_color_brewer是对ggplot中的color指标作出的格式方案，和color是谁没有关系。
```

***

### Clarity and Price
Response:

***

### Price vs. Carat and Cut

Alter the code below.
```{r Price vs. Carat and Cut}
ggplot(aes(x = carat, y = price, color = clarity), data = diamonds) + 
  geom_point(alpha = 0.5, size = 1, position = 'jitter') +
  scale_color_brewer(type = 'div',
                     guide = guide_legend(title = 'Clarity', reverse = T,
                                          override.aes = list(alpha = 1, size = 2))) +  
  scale_x_continuous(trans = cuberoot_trans(), limits = c(0.2, 3),
                     breaks = c(0.2, 0.5, 1, 2, 3)) + 
  scale_y_continuous(trans = log10_trans(), limits = c(350, 15000),
                     breaks = c(350, 1000, 5000, 10000, 15000)) +
  ggtitle('Price (log10) by Cube-Root of Carat and Clarity')
```

***

### Cut and Price
Response:

***

### Price vs. Carat and Color

Alter the code below.
```{r Price vs. Carat and Color}

ggplot(aes(x = carat, y = price, color = clarity), data = diamonds) + 
  geom_point(alpha = 0.5, size = 1, position = 'jitter') +
  scale_color_brewer(type = 'div',
                     guide = guide_legend(title = 'c', reverse = T,
                                          override.aes = list(alpha = 1, size = 2))) +  
  scale_x_continuous(trans = cuberoot_trans(), limits = c(0.2, 3),
                     breaks = c(0.2, 0.5, 1, 2, 3)) + 
  scale_y_continuous(trans = log10_trans(), limits = c(350, 15000),
                     breaks = c(350, 1000, 5000, 10000, 15000)) +
  ggtitle('Price (log10) by Cube-Root of Carat and Clarity')
#guide中的title = 就是起了一个名字，和数据没有关系。要加‘’。

ggplot(aes(x = carat, y = price, color = cut), data = diamonds) + 
  geom_point(alpha = 0.5, size = 1, position = 'jitter') +
  scale_color_brewer(type = 'div',
                     guide = guide_legend(title = 'cut', reverse = T,
                                          override.aes = list(alpha = 1, size = 2))) +  
  scale_x_continuous(trans = cuberoot_trans(), limits = c(0.2, 3),
                     breaks = c(0.2, 0.5, 1, 2, 3)) + 
  scale_y_continuous(trans = log10_trans(), limits = c(350, 15000),
                     breaks = c(350, 1000, 5000, 10000, 15000)) +
  ggtitle('Price (log10) by Cube-Root of Carat and Cut')

#价格+克拉+颜色
ggplot(aes(x = carat, y = price, color = color), data = diamonds) + 
  geom_point(alpha = 0.5, size = 1, position = 'jitter') +
  scale_color_brewer(type = 'div',
                     guide = guide_legend(title = 'Color', reverse = F,
                                          override.aes = list(alpha = 1, size = 2))) +  
  scale_x_continuous(trans = cuberoot_trans(), limits = c(0.2, 3),
                     breaks = c(0.2, 0.5, 1, 2, 3)) + 
  scale_y_continuous(trans = log10_trans(), limits = c(350, 15000),
                     breaks = c(350, 1000, 5000, 10000, 15000)) +
  ggtitle('Price (log10) by Cube-Root of Carat and Color')
```

***

### Color and Price
Response:

***

### Linear Models in R
Notes:

Response:

***

### Building the Linear Model
Notes:

```{r Building the Linear Model}
m1 <- lm(I(log(price)) ~ I(carat^(1/3)), data = diamonds)
m2 <- update(m1, ~ . + carat)
m3 <- update(m2, ~ . + cut)
m4 <- update(m3, ~ . + color)
m5 <- update(m4, ~ . + clarity)
mtable(m1, m2, m3, m4, m5)
#模型问题
#https://classroom.udacity.com/nanodegrees/nd002-cn-advanced/parts/e4f6345b-a3a9-451e-8d69-d555941703bd/modules/a1a7933c-f014-4d05-be69-682856b8b300/lessons/755209509/concepts/8624987670923
```

Notice how adding cut to our model does not help explain much of the variance
in the price of diamonds. This fits with out exploration earlier.

***

### Model Problems
Video Notes:

Research:
(Take some time to come up with 2-4 problems for the model)
(You should 10-20 min on this)

Response:

***

### A Bigger, Better Data Set
Notes:

```{r A Bigger, Better Data Set}
install.packages('bitops')
install.packages('RCurl')
library('bitops')
library('RCurl')

#diamondsurl = getBinaryURL("https://raw.github.com/solomonm/diamonds-data/master/BigDiamonds.Rda")
#load(rawConnection(diamondsurl))
library(rstudioapi)
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
load('BigDiamonds.rda')

#https://classroom.udacity.com/nanodegrees/nd002-cn-advanced/parts/e4f6345b-a3a9-451e-8d69-d555941703bd/modules/a1a7933c-f014-4d05-be69-682856b8b300/lessons/755209509/concepts/8624987700923#
#之前的无效，使用注释中的内容

diamondsbig$logprice = log(diamondsbig$price)

head(diamondsbig$cert)

m1 <- lm(logprice ~ I(carat^(1/3)), data = diamondsbig[diamondsbig$price < 10000 & diamondsbig$cert == "GIA",])
#&为和，|或。开始$打错了。也没有筛选出来，还是53940个。后续研究。'和"没有区别。
m2 <- update(m1, ~ . + carat)
m3 <- update(m2, ~ . + cut)
m4 <- update(m3, ~ . + color)
m5 <- update(m4, ~ . + clarity)
mtable(m1, m2, m3, m4, m5)
```

The code used to obtain the data is available here:
https://github.com/solomonm/diamonds-data

## Building a Model Using the Big Diamonds Data Set
Notes:

```{r Building a Model Using the Big Diamonds Data Set}

```


***

## Predictions

Example Diamond from BlueNile:
Round 1.00 Very Good I VS1 $5,601

```{r}
#Be sure you’ve loaded the library memisc and have m5 saved as an object in your workspace.
thisDiamond = data.frame(carat = 1.00, cut = "V.Good",
                         color = "I", clarity="VS1")
modelEstimate = predict(m5, newdata = thisDiamond,
                        interval="prediction", level = .95)
modelEstimate
#没懂，项目中再想。

#更好的数据
dat = data.frame(m4$model, m4$residuals) 
with(dat, sd(m4.residuals)) 
with(subset(dat, carat > .9 & carat < 1.1), sd(m4.residuals)) 
dat$resid <- as.numeric(dat$m4.residuals)
ggplot(aes(y = resid, x = round(carat, 2)), data = dat) + geom_line(stat = "summary", fun.y = sd) 
```

Evaluate how well the model predicts the BlueNile diamond's price. Think about the fitted point estimate as well as the 95% CI.

***

## Final Thoughts
Notes:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

